\renewcommand{\bibname}{Litteraturliste}
\fancyhead[CE,CO]{}
\fancyfoot[CE,CO]{}
\begin{thebibliography}{2}
\hbadness=10000
%SKABELON*** \bibitem{lib:##REF##} ##FIRMANAVN##: \textit{##FORKLARING##}. \\ ##\URL{} ELLER BILAG XXX??##. ##DATO##

\bibitem {lib:MIPICSI-2} MIPI Alliance, Inc.: \textit{Camera Interface Specifications}. \\ 
\url{http://mipi.org/specifications/camera-interface}. 14. december 2015.

\bibitem {lib:PI2PSU} RASPBERRY PI FOUNDATION: \textit{POWER}. \\
\url{https://www.raspberrypi.org/help/faqs/#powerReqs}. 14. december 2015.

\bibitem {lib:maxsonar} MaxBotix Inc.: \textit{I2CXL-MaxSonar - EZ Series datablad}. \\
"Bilag 011 - 1202\_MaxSonar". 2012.

\bibitem{lib:servo} Corano: \textit{CS238MG Metal Gear Servo datablad}\\
"Bilag 006 - CS238MG". Dato ukendt.

\bibitem {lib:accel} InvenSense Inc.: \textit{MPU-6000 and MPU-6050 Product Specification Revision 3.4 datablad}. \\
"Bilag 014 - MPU-6000-Datasheet1". 2. oktober 2015.

\bibitem {lib:tacho} SIEMENS: \textit{TLE4905L Hall Switch datablad}. \\
"Bilag 015 - hall datasheet". 1. september 1997.

\bibitem {lib:psu_L1core} EPCOS: \textit{Ferrites and accessories, ETD 29/16/10, Core and accessories datablad}. \\
"Bilag 016 - ETD spolekerne datasheet". April 2015.

\bibitem {lib:psu_calcs} Kristian Thomsen: \textit{Beregninger for bilens strømforsyning}. \\
"Bilag 005 - PSU\_udregninger". 11. december 2015.

\bibitem {lib:analogteknik} Tore Skogberg: \textit{Analogteknik T-005 v1.2}.\\
"Bilag 009 - Analogteknik v1-2". 2015.

\bibitem {lib:lm26003} Texas Instruments: \textit{LM26003 datablad}. \\
"Bilag 012 - lm26003". Februar 2015.

\bibitem {lib:vlc-ftp} VideoLAN: \textit{VLC Mediaplayer plugins}. \\
\url{ftp://ftp.videolan.org/pub/videolan/vlc/2.0.7/win32/}. 14. december 2015.

\bibitem {lib:qt} The Qt Company: \textit{Qt Creator}. \\
\url{http://www.qt.io/ide/} 14. december 2015.

\bibitem {lib:vlc-qt} Tadej Novak: \textit{Quickly create a fully functional cross-platform media player}. \\
\url{https://vlc-qt.tano.si/} 14. december 2015.

\bibitem {lib:vlc-using-qt} Derek Molloy: \textit{Custom Video Streaming Player using LibVLC and Qt}. \\
\url{http://derekmolloy.ie/custom-video-streaming-player-using-libvlc-and-qt/} 14. december 2015.

\bibitem {lib:qt-bog} Jasmin Blanchette, Mark Summerfield: \textit{C++ GUI Programming with Qt 4, Second Edition} \\
"Bilag 013 - c-gui-programming-with-qt-4-2ndedition". Februar 2008.

\bibitem {lib:motion-on-raspberry} captain-slow.dk: \textit{Install Motion on a Raspberry Pi}. \\
\url{http://captain-slow.dk/2013/11/01/install-motion-on-a-raspberry-pi/}. 13. december 2015

\bibitem {lib:motion-on-raspberry2} OSMC forums: \textit{Trying to install motion - missing libs}. \\
\url{https://discourse.osmc.tv/t/trying-to-install-motion-missing-libs/5709/9} 14. december 2015.

\bibitem {lib:camera-driver} linux-projects.org: \textit{uv4l Camera driver}. \\
\url{http://www.linux-projects.org/modules/sections/index.php?op=viewarticle&artid=14} 14. december 2015.

\bibitem {lib:wikiPWM} Wikipedia: \textit{PWM}.\\
\url{https://en.wikipedia.org/wiki/Pulse-width_modulation}. 14. december 2015.

\bibitem {lib:L298N_datablad} STMicroelectronics: \textit{L298N datablad}. \\
"Bilag 004 - L298N datablad". Januar 2000.

\bibitem {lib:wikiHbro} Wikipedia: \textit{H bridge}.\\
\url{https://en.wikipedia.org/wiki/H_bridge}. 10. December 2015.

\bibitem {lib:wiki-RC-Servo} Wikipedia: \textit{Servo control}. \\
\url{https://en.wikipedia.org/wiki/Servo_control}. 10. December 2015.

\bibitem {lib:xboxcontroller} Project Reality: Realistic Gaming Redefined: \textit{Xbox 360 controller on PR/BF2}. \\
\url{http://www.realitymod.com/forum/f10-pr-bf2-general-discussion/108237-xbox-360-controller-pr-bf2.html}. 10. december 2015.

\bibitem {lib:RUC} Rasmus Karkov: \textit{Voksne skal forstå børns leg med teknik}. \\
\url{https://www.ruc.dk/om-universitetet/nyhedsportal/rubrik-forskningsmagasin/rubrik-nr-6/voksne-skal-forstaa-boerns-leg-med-teknik/}. 10. december 2015.

\bibitem {lib:GNU_make} Free Software Foundation, Inc.: \textit{GNU Make}. \\
\url{https://www.gnu.org/software/make/}. 14. december 2015.

%TODO -------------------------------- Er disse to henvisninger korrekte? /PKP
\bibitem {lib:wiringpi} Gordon Henderson: \textit{Github for WiringPi library}. \\
\url{https://github.com/raspberrypi/tools}. 14. december 2015.

\bibitem {lib:pi_tools} RASPBERRY PI FOUNDATION: \textit{GPIO interface for the Raspberry Pi}. \\
\url{http://wiringpi.com/download-and-install/}. 14. december 2015.
%TODO ---------------------------------

\bibitem {lib:wiringpi_projekt} WiringPi: \textit{WiringPi}. \\
\url{http://wiringpi.com}. 13. december 2015.

\bibitem {lib:PREEMPT_RT} EMLID: \textit{PREEMPT\_RT}. \\
\url{http://docs.emlid.com/Downloads/Real-time-Linux-RPi2/}. 14. december 2015.

\bibitem {lib:raspbian} Raspbian: \textit{Raspbian}. \\
\url{https://www.raspbian.org/}. 14. december 2015.

\bibitem {lib:rpi_sd} Embedded Linux Wiki: \textit{RPi Easy SD Card Setup}. \\
\url{http://elinux.org/RPi_Easy_SD_Card_Setup#Flashing_the_SD_Card_using_Windows}. 14. december 2015.

\bibitem {lib:ssh} MELTWATER'S RASPBERRY PI HARDWARE: \textit{Raspberry Pi Remote Connections – Without A Network!}. \\
\url{https://pihw.wordpress.com/guides/direct-network-connection/}. 14. december 2015.

\end{thebibliography}
